Case Study: 16S microbiome data (Schubert et al., 2014)

### 2018-06-24 datasets/microbiome/microbiome-baxter.Rmd
Add method heatmaps to case studies with more than one covariate/comparison
Add mean abundance covariate

>>>>

## Multiple-Testing Correction - mean abundance

Let's use `mean_abun_present` as our `ind_covariate`.

```{r, baxter-genus-labelcovariate-abun}
res <- dplyr::mutate(res, ind_covariate = mean_abun_present)
```

```{r, baxter-genus-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/crc_baxter_results.tar.gz"
    saveRDS(sb, file = gns_bench_file_abun)
} else {
    sb <- readRDS(gns_bench_file_abun)
}
```

# OTU/Genus comparison

Here we compare the method ranks for the different comparisons at alpha = 0.10.

```{r, eval = FALSE}
plotMethodRanks(c(otu_bench_file, otu_bench_file_log_ubiquity, 
                  gns_bench_file, gns_bench_file_log_ubiquity), 
                colLabels = c("OTU", "OTU - log", "Genus", "Genus - log"), 
                alpha = 0.10, xlab = "Comparison")
```

### 2018-06-24 datasets/microbiome/microbiome-enigma.Rmd
Add mean abundance covariate

# From their paper, we expect SO4 to have little correlation, pH
# to have high correlations, and Al to be in the middle
so4_result_file <- file.path(resdir, "enigma-so4-otus-results.rds")
so4_bench_file <- file.path(sbdir, "enigma-so4-otus-benchmark.rds")

ph_result_file <- file.path(resdir, "enigma-ph-otus-results.rds")
ph_bench_file <- file.path(sbdir, "enigma-ph-otus-benchmark.rds")

al_result_file <- file.path(resdir, "enigma-al-otus-results.rds")
al_bench_file <- file.path(sbdir, "enigma-al-otus-benchmark.rds")
```

@@

@@

@@

>>>>

# From their paper, we expect SO4 to have little correlation, pH
# to have high correlations, and Al to be in the middle
so4_result_file <- file.path(resdir, "enigma-so4-otus-results.rds")
so4_bench_file <- file.path(sbdir, "enigma-so4-otus-benchmark.rds")
so4_bench_file_abun <- file.path(sbdir, "enigma-so4-otus-abun-benchmark.rds")

ph_result_file <- file.path(resdir, "enigma-ph-otus-results.rds")
ph_bench_file <- file.path(sbdir, "enigma-ph-otus-benchmark.rds")
ph_bench_file_abun <- file.path(sbdir, "enigma-ph-otus-abun-benchmark.rds")

al_result_file <- file.path(resdir, "enigma-al-otus-results.rds")
al_bench_file <- file.path(sbdir, "enigma-al-otus-benchmark.rds")
al_bench_file_abun <- file.path(sbdir, "enigma-al-otus-abun-benchmark.rds")
```

@@

### Multiple-Testing Correction - mean abundance

Let's use `mean_abun_present` as our `ind_covariate`.

```{r, ph-labelcovariate-abun}
res <- dplyr::mutate(res, ind_covariate = mean_abun_present)
```

```{r, ph-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(ph_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = ph_bench_file_abun)
} else {
    sb <- readRDS(ph_bench_file_abun)
}
```

@@

### Multiple-Testing Correction - mean abundance

Let's use `mean_abun_present` as our `ind_covariate`.

```{r, so4-labelcovariate-abun}
res <- dplyr::mutate(res, ind_covariate = mean_abun_present)
```

```{r, so4-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(so4_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = so4_bench_file_abun)
} else {
    sb <- readRDS(so4_bench_file_abun)
}
```

@@

### Multiple-Testing Correction - mean abundance

Let's use `mean_abun_present` as our `ind_covariate`.

```{r, al-labelcovariate-abun}
res <- dplyr::mutate(res, ind_covariate = mean_abun_present)
```

```{r, al-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(al_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = al_bench_file_abun)
} else {
    sb <- readRDS(al_bench_file_abun)
}
```

# Response comparison

Here we compare the method ranks for the different comparisons at alpha = 0.10.

```{r, eval = FALSE}
plotMethodRanks(c(so4_bench_file, ph_bench_file, al_bench_file), 
                colLabels = c("SO4", "pH", "Al"), 
                alpha = 0.10, xlab = "Comparison")
```

### 2018-06-24 datasets/microbiome/microbiome-goodrich.Rmd
Add method heatmaps to case studies with more than one covariate/comparison
Add mean abundance covariate

otu_result_file <- file.path(resdir, "goodrich-otus-results.rds")
otu_bench_file <- file.path(sbdir, "goodrich-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "goodrich-genus-results.rds")
gns_bench_file <- file.path(sbdir, "goodrich-genus-benchmark.rds")
```

@@

>>>>

otu_result_file <- file.path(resdir, "goodrich-otus-results.rds")
otu_bench_file <- file.path(sbdir, "goodrich-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "goodrich-genus-results.rds")
gns_bench_file <- file.path(sbdir, "goodrich-genus-benchmark.rds")
gns_bench_file_abun <- file.path(sbdir, "goodrich-genus-abun-benchmark.rds")
```

@@

## Multiple-Testing Correction - mean abun

Let's use `mean_abun_present` as our `ind_covariate`.

```{r, goodrich-genus-labelcovariate-abun}
res <- dplyr::mutate(res, ind_covariate = mean_abun_present)
```

```{r, goodrich-genus-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ob_goodrich_results.tar.gz"
    saveRDS(sb, file = gns_bench_file_abun)
} else {
    sb <- readRDS(gns_bench_file_abun)
}
```

# OTU/Genus comparison

Here we compare the method ranks for the different comparisons at alpha = 0.10.

```{r, eval = FALSE}
plotMethodRanks(c(otu_bench_file, gns_bench_file), 
                colLabels = c("OTU", "Genus"), 
                alpha = 0.10, xlab = "Comparison")
```

### 2018-06-24 datasets/microbiome/microbiome-papa.Rmd
Add method heatmaps to case studies with more than one covariate/comparison
Add mean abundance covariate

otu_result_file <- file.path(resdir, "papa-otus-results.rds")
otu_bench_file <- file.path(sbdir, "papa-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "papa-genus-results.rds")
gns_bench_file <- file.path(sbdir, "papa-genus-benchmark.rds")
gns_bench_file_log_ubi <- file.path(resdir, "papa-genus-log-ubiquity-benchmark.rds")
```

@@

>>>>

otu_result_file <- file.path(resdir, "papa-otus-results.rds")
otu_bench_file <- file.path(sbdir, "papa-otus-benchmark.rds")
gns_result_file <- file.path(resdir, "papa-genus-results.rds")
gns_bench_file <- file.path(sbdir, "papa-genus-benchmark.rds")
gns_bench_file_log_ubi <- file.path(resdir, "papa-genus-log-ubiquity-benchmark.rds")
gns_bench_file_abun <- file.path(resdir, "papa-genus-abun-benchmark.rds")
```

@@

## Multiple-Testing Correction - mean abundance

Let's use `mean_abun_present` as our `ind_covariate`.

```{r, papa-genus-labelcovariate-abun}
res <- dplyr::mutate(res, ind_covariate = mean_abun_present)
```

```{r, papa-genus-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ibd_alm_results.tar.gz"
    saveRDS(sb, file = gns_bench_file_abun)
} else {
    sb <- readRDS(gns_bench_file_abun)
}
```

# OTU/Genus comparison

Here we compare the method ranks for the different comparisons at alpha = 0.10.

```{r, eval = FALSE}
plotMethodRanks(c(otu_bench_file, gns_bench_file, gns_bench_file_log_ubi), 
                colLabels = c("OTU", "Genus", "Genus - log ubiquity"), 
                alpha = 0.10, xlab = "Comparison")
```

### 2018-06-24 datasets/microbiome/microbiome-schubert.Rmd
Add mean abundance covariate

otu_result_file <- file.path(resdir, "schubert-otus-results.rds")
otu_bench_file <- file.path(sbdir, "schubert-otus-benchmark.rds")
```

@@

>>>>

otu_result_file <- file.path(resdir, "schubert-otus-results.rds")
otu_bench_file <- file.path(sbdir, "schubert-otus-benchmark.rds")
otu_bench_file_abun <- file.path(sbdir, "schubert-otus-abun-benchmark.rds")
```

@@

## Multiple-Testing Correction - mean abundance

Let's use `mean_abun_present` as our `ind_covariate`.

```{r, schubert-labelcovariate-abun, eval=TRUE}
res <- dplyr::mutate(res, ind_covariate = mean_abun_present)
```

```{r, schubert-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(otu_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/cdi_schubert_results.tar.gz"
    saveRDS(sb, file = otu_bench_file_abun)
} else {
    sb <- readRDS(otu_bench_file_abun)
}
```
